\documentclass[11pt]{article}
\usepackage{url}


\usepackage[ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{color}

\author{Christian Kniep}
\title{Advanced Operating System with UNIX Exam}
\date{\today}
%----------------------------
\begin{document}
\maketitle
\section*{UNIX Test}
If there is now value in braces then you will earn 1 point per default
\subsection*{UNIT 1 Review OS}
\begin{enumerate}
    \item What is the purpose of an OS (operating system)? \\
    \\
    \\
    \item What is the central thing most operating systems have in common? Even if they called it different. \\
    \\    
\end{enumerate}

\newpage
\subsection*{UNIT 2 File System}
\begin{enumerate}
    \item Please draw an example file-system tree, with at least two standard directorys and one file. \\
    \\
    \\
    \\
    \\
    \\
    \\
    \item What is the swap for? \\
    \\
    \\
    \\
    \\
    \item Give a short explanation about the connections between 'Blocks', 'INodes', 'Filenames'.\\
    \\
    \\
    \\
    \item Why do we need fsck (File System Check)? \\
    \\
    \\
    \\    
\end{enumerate}

\newpage
\subsection*{UNIT 3 Processes}
\begin{enumerate}
    \item Explain at least three of this process-attributes:
    \begin{itemize}
        \item UID
        \item EUID
        \item PID
        \item PPID
        \item GID
        \item PRI
    \end{itemize}
    \item What is a child? \\
    \\
    \\
    \item What is a zombie State? \\
    \\
    \\
    \item Explain at least three of the following interprocess comunication techniques:
    \begin{itemize}
        \item Pipes
        \item Named Pipes
        \item Message queues
        \item Semaphores
        \item Shared Memory
        \item Sockets
    \end{itemize}
\end{enumerate}

\newpage
\subsection*{UNIT 4 Begining with UNIX}
\begin{enumerate}
    \item Where do you find the central file which holds the basic user information? \\
    \\
    \item Why is it clever to have permissions? \\
    \\
    \\
    \item What is the difference between the output redirection with '\textgreater','\textgreater\textgreater', '1\textgreater' and '2\textgreater' \\
    \\
    \\
    \item What is the purpose of the environment? \\
    \\
    \\
    \\
\end{enumerate}

\newpage
\subsection*{UNIT 5 UNIX File System}
\begin{enumerate}
    \item Write down the commands to... (the names are free to choose)
    \begin{itemize}
        \item create a directory in your home-directory (make sure you are there)
        \item create a file within the created directorys
        \item rename the file
        \item delete the created directory
    \end{itemize}
    \item What are the three types of UNIX files? \\
    \\
    \\
    \\
    \item How to change the permissions of file to the following:
    \begin{enumerate}
        \item \texttt{rwxrw-rw-}: \texttt{\$}
        \item \texttt{rwx------}: \texttt{\$}
        \item \texttt{rw-r--r--}: \texttt{\$}
    \end{enumerate}
    \item What is the umask? \\
    \\
    \\
\end{enumerate}

\newpage
\subsection*{UNIT 6 Managing Data files in UNIX}
\begin{enumerate}
    \item What is the difference between 'ls' and 'ls -l'? \\
    \\
    \\
    \\
    \item Give a short description of the different blocks of this output: \\
    \texttt{-rwxr-xr-x 2 test test 296 2010-08-03 13:58 file} \\
    \\
    \\
    \\
    \\
    \item PatternMatching:
    \begin{itemize}
        \item Please list for all files that starts with 'file'. \\
        \\
        \item Please list all files that have \textbf{one} unknown character in front of 'file' (e.g. '1file'). \\
        \\
        \item Please create a listing command which includes the files 'file.txt', 'file.doc' and 'file.cfg'. \\
        \\
    \end{itemize}
    \item How could you locate files with various search criterias? \\
    \\
\end{enumerate}

\newpage
\subsection*{UNIT 7 Popular Tools in UNIX}
\begin{enumerate}
    \item Calculate '1+4' with bc (you start in bash and could use a pipe or the command itself).
    \item Calculate '2/1' with bc (you have to set one position after decimal point)
    \item How could you get the current time and date.
    \item What information do you get if you type 'whoami'?
    \item What are the two ways to get information about a command and what is the difference?
\end{enumerate}
    
\end{document}