\documentclass[hyperref={pdfpagelabels=false}]{beamer}
%\documentclass[handout]{beamer}
\let\Tiny=\tiny
\hypersetup{pdfpagemode=FullScreen}
\usepackage[ngerman]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage{listings}
\usepackage{verbatim}
%\setbeamertemplate{navigation symbols}{}

\usetheme{Boadilla}

\usecolortheme{beaver}
\usefonttheme{professionalfonts}
\useinnertheme{rounded}
\useoutertheme{smoothbars}
%\useoutertheme{sidebar}

\definecolor{lGray}{gray}{.90}

\newcommand{\code}[1]{\colorbox{lGray}{\texttt{#1}}}
\author{Christian Kniep}

\begin{document}
\title{Advanced Operating System with UNIX \\ Unit 4 - Getting Started}  
\institute[ICAT Bandung]{Internation Center of Applied Technologies Bandung}
\date[\today]{\today} 

\begin{frame}
	\titlepage
\end{frame} 


\section{Introduction} 
	\subsection{User Account Setup}
		\begin{frame}{Why you are able to work with the System}
			\begin{itemize}
				\item<1-> Please read Section 4.1 and 4.1.1
                \item<2-> What is a username?
                \item<3-> What the deal with the initial password?
            \end{itemize}
		\end{frame}
	\subsection{Logging in}
		\begin{frame}{Log onto the machine}
			\begin{itemize}
				\item<1-> Please read Section 4.1.2
                \item<2-> Why is your password not shown when you type it, \\
                            Windows has at least asterisks?
                \item<3-> \code{gray:*:1001:1001:Gray Ho:/home/gray:/bin/bash} \\
                            What is the Problem if you get
                \begin{itemize}
                    \item<4-> \code{Could not chdir /home/test: No such file or directory}
                    \item<5-> \code{Permission denied, please try again.}
                    \item<6-> \code{ssh\_exchange\_identification: Connection closed}
                \end{itemize}
            \end{itemize}
		\end{frame}
	\subsection{Login Succeeds}
		\begin{frame}{Whats next}
			\begin{itemize}
				\item<1-> Please read Section 4.1.3
                \item<2-> Whats the 'Message Of The Day'
                \item<3-> What other messages could appear?
                \item<4-> What is the 'prompt'
                \item<5-> PS1?
            \end{itemize}
		\end{frame}
\section{Different Privileges}
    \subsection{Short}
    	\begin{frame}{Privileges and Permissions}
			\begin{itemize}
				\item<1-> Please read Section 4.2
                \item<2-> Why do we want different Privileges?
                \item<3-> What permissions-triples do you know?
            \end{itemize}
		\end{frame}
\section{Logging Out}
    \subsection{Short}
    	\begin{frame}{Getting stoped}
			\begin{itemize}
				\item<1-> Please read Section 4.3
                \item<2-> What are possible ways to get out?
            \end{itemize}
		\end{frame}
\section{Using Commands}
    \subsection{Introduction}
    	\begin{frame}{what to do?}
			\begin{itemize}
				\item<1-> Please read Section 4.4
                \item<2-> Why do you need commands?
            \end{itemize}
        \end{frame}
    \subsection{What Is a Command?}
    	\begin{frame}{definition?}
			\begin{itemize}
				\item<1-> Please read Section 4.4.1
                \item<2-> What is it?
                \item<3-> What are common options for \code{ls}
            \end{itemize}
		\end{frame}
    \subsection{Redirecting Input and Output}
    	\begin{frame}{stdin - stdout}
			\begin{itemize}
				\item<1-> Please read Section 4.4.2
                \item<2-> Who wants to try it?
            \end{itemize}
		\end{frame}
    \subsection{Configuring Your Environment}
    	\begin{frame}{Introduction,Viewing and Setting the Environment}
			\begin{itemize}
				\item<1-> Please read Section 4.4.3 and 4.4.3.1
                \item<2-> What is the environment?
                \item<3-> Why do we need it?
                \item<4-> how could you have a look at it?
            \end{itemize}
		\end{frame}
    \subsection{Using Shell Startup Files}
    	\begin{frame}{bashrc and alike}
			\begin{itemize}
				\item<1-> Please read Section 4.4.3.2
                \item<2-> Whats the advantage of the startup-scripts?
            \end{itemize}
		\end{frame}
    \subsection{Configuring with rc files}
    	\begin{frame}{The hidden setting}
			\begin{itemize}
				\item<1-> Please read Section 4.4.3.3
                \item<2-> Why is it clever to store the settings of your user in your home-dir?
                \item<3-> What is the advantage when you have multiple machine and a central home?
            \end{itemize}
		\end{frame}
    \subsection{Managing Your Password}
    	\begin{frame}{Safty First!}
			\begin{itemize}
				\item<1-> Please read Section 4.5
                \item<2-> Who you gonna tell the password?
                \item<3-> Some strategies to avoid easy to guess PW?
                \item<4-> Tipp: Use first chars out of sentences. \\
                 \textbf{M}y \textbf{p}assword \textbf{1}s \textbf{s}ecure. \textbf{N}obody \textbf{w}ill \textbf{g}uess \textbf{1}t.
                \item[$\Rightarrow$]<5-> Mp1sNwg1
            \end{itemize}
		\end{frame}
    \subsection{control characters}
    	\begin{frame}{Some special chars}
			\begin{itemize}
				\item<1-> Please read Section 4.6 and 4.6.*
                \item<2-> What are these special chars for?
                \item<3-> In my Opinion the most used: \code{ctrl-C} and \code{ctrl-D}
            \end{itemize}
		\end{frame}
    \subsection{Online Help}
    	\begin{frame}{Help, I need somebody..}
			\begin{itemize}
				\item<1-> Please read Section 4.7
                \item<2-> What are the two ways to get help?
                \item<3-> whats teh man page?
                \item<4-> and \code{--help} / \code{-h} or \code{-?}?
                \item<5-> \code{man -k}?
            \end{itemize}
		\end{frame}


\end{document}
